---
title: "EEGMoralization"
author: "Keith J. Yoder"
date: "April 23, 2021"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
  html_notebook:
    toc: yes
    toc_depth: 3
---

```{r setup, include=FALSE}
require(tidyverse)
require(lme4)
require(sjPlot)
require(sjstats)
require(effectsize)
require(parameters)
require(emmeans)
require(afex)

set_theme(theme_classic())
```



# Helper functions
```{r helper_funcs}
mixed_summary <- function(x) {
  val <- x$anova_table
  val$Parameter <- rownames(val)
  val <- val %>% select(Parameter, everything())
  return(val)
}

model_summary <- function(x) {
  params <- model_parameters(x)
  std <- standardize_parameters(x) %>%
    rename(std_low = CI_low) %>%
    rename(std_high = CI_high)
  
  mod_sum <- bind_cols(params['Parameter'], params['Coefficient'], 
                       params['CI_low'], params['CI_high'], std['Std_Coefficient'], 
                       std['std_low'], std['std_high'],
                       params['t'], params['p'])
  
  return(mod_sum)
}

eeg_summary <- function(x) {
  params <- model_parameters(x)
  std <- standardize_parameters(x) %>%
    rename(std_low = CI_low) %>%
    rename(std_high = CI_high)
  
  mod_sum <- bind_cols(params['Parameter'], params['Coefficient'], 
                       params['CI_low'], params['CI_high'], params['p'], std['Std_Coefficient'])
  
  return(mod_sum)
}

vif.mer <- function(fit) {
  # https://github.com/aufrank/R-hacks/blob/master/mer-utils.R
  v <- vcov(fit)
  nam <- names(fixef(fit))
  ## exclude intercepts
  ns <- sum(1 * (nam == "Intercept" | nam == "(Intercept)"))
  if (ns > 0) {
    v <- v[-(1:ns), -(1:ns), drop = FALSE]
    nam <- nam[-(1:ns)] }
  d <- diag(v)^0.5
  v <- diag(solve(v/(d %o% d)))
  names(v) <- nam
  return(v)
}
```


# Behavioral 

## Import data
```{r import_data1}
data_beh <- read_rds("data/data_beh.RDS")
data_issues <- read_rds("data/data_issues.RDS")
```

## Summarize Issues
```{r summarize_issues}
issue_sub <- data_issues %>% 
  select(SubjectID, MC, Polarized) %>%
  group_by(SubjectID) %>%
  summarize(Polarized = mean(Polarized, na.rm=TRUE), 
            MC = mean(MC, na.rm=TRUE))

iss_avg.mod <- lmer(MC ~ 1 + (1|IssueShort) + (1|SubjectID), data = data_issues)
iss_avg.int <- fixef(iss_avg.mod)
iss_avg.iss <- ranef(iss_avg.mod)$IssueShort
iss_avg <- iss_avg.iss + iss_avg.int
iss_avg$IssueShort <- rownames(iss_avg)

iss_avg <- iss_avg %>%
  rename(AvgMC = "(Intercept)")

ggplot(iss_avg, aes(reorder(IssueShort, AvgMC), AvgMC, fill=AvgMC)) +
  geom_bar(stat="identity") + 
  scale_fill_viridis_c() +
  theme(legend.position="bottom")+
  labs(x=NULL, y="Mean rating", fill="Moral Conviction") +
  coord_flip() 
```

## Polarization, MC, and meta-d'
```{r init_ratings}
mc_meta <- data_beh %>%
  select(SubjectID, Issue, Polarized, MC, meta_d) %>%
  drop_na() %>%
  unite(SI, SubjectID, Issue, remove=FALSE) %>%
  filter(!duplicated(select(., SI)))

mc_meta.polarized <- lmer(Polarized ~ MC + meta_d + (1|SubjectID) + (1|Issue), data=mc_meta)
#model_summary(mc_meta.polarized)
```

## Responses
```{r resps}
resp_base<- mixed(Response_scale ~ (PriorSupport_scale + SocialSupport.f + ProtestOppose.f)^3 +
                    + Age.z + Female + (SocialSupport.f | SubjectID) + (1 | Issue),
                  data = data_beh, control=lmerControl(optimizer="bobyqa"), method="PB")
#model_summary(resp_base)

mixed_summary(resp_base) %>% write_csv("Table_beh1_support.csv")
```


```{r resp_posthoc}
trend.mod <- emtrends(resp_base, ~  ProtestOppose.f, "PriorSupport_scale",
                      at = c(list(PriorSupport_scale = seq(-1, 1))),
                      options = list(), lmer.df = 'satterthwaite')
summary(trend.mod, infer=c(TRUE, TRUE), null = 0)
```

## Aligned responses
```{r aligned_resp}
resp_align_sig <- mixed(CurrentSupport ~ (PriorSupport_scale + MajoritySupport.f +
                  MC.z + meta_d )^3 + Age.z + Edu.z + Income.z + Female
                + (MajoritySupport.f | SubjectID) + (1 | Issue),
                  data = data_beh, control=lmerControl(optimizer="bobyqa"), method="PB")
resp_align <- lmer(CurrentSupport ~ (PriorSupport_scale + MajoritySupport.f +
                  MC.z + meta_d )^3 + Age.z + Edu.z + Income.z + Female
                + (MajoritySupport.f | SubjectID) + (1 | Issue),
                  data = data_beh, control=lmerControl(optimizer="bobyqa"))
#model_summary(resp_align_sig)

mixed_summary(resp_align_sig) %>% write_csv("Table_beh2_alignresp.csv")
```


```{r fig2a}
p1<-plot_model(resp_align, type="eff", terms=c("PriorSupport_scale", "MC.z[-1,1]", "MajoritySupport.f"),
           title = "Moral Conviction and Majority Support") +
  geom_hline(yintercept = 0, alpha=.3) + geom_vline(xintercept = 0, alpha=.3)+
  labs(x="Prior Support", y="Current Support", col = "MC")

p1$data$facet <- factor(p1$data$facet, c("Minority","Neutral","Majority"))
p1$data$group <- factor(p1$data$group, levels=c(-1,1),
                        labels=c("-1 SD", "+1 SD"))
p1 +
  labs(x = "Scaled Prior Support", y = "Scaled Rating", color="MC")
```

```{r fig2b}
p1<- plot_model(resp_align, type="eff", terms=c("PriorSupport_scale", "MC.z[-1,1]", "meta_d[-.5,.5]"),
           title="Moral Conviction * Meta-d'") +
  geom_hline(yintercept = 0, alpha=.3) + geom_vline(xintercept = 0, alpha=.3) +
  labs(x = "Prior Support", y="Current Support", col = "MC")

p1$data$facet <- factor(p1$data$facet, levels=c(-.5, .5),
                        c("meta-d: -1 SD", "meta-d: +1 SD"))
p1$data$group <- factor(p1$data$group, levels=c(-1,1),
                        labels=c("-1 SD", "+1 SD"))
p1 +
  labs(x = "Scaled Prior Support", y = "Scaled Rating", color="MC")
```

## Conformity
```{r conf}
merged_m <- data_beh %>%
  select(Conformity, Polarized, Polarized.z, MajoritySupport.f, meta_d,
         MC.z, MC, Moral, Moral.f, Age.z, Edu.z, Income.z, Female, SubjectID, Issue,
         ProtestOppose.f) %>%
  drop_na()

conf_mod_sig <- mixed(Conformity ~  (MC.z + MajoritySupport.f + meta_d)^3 +
                     Polarized.z * MajoritySupport.f +
                   Age.z + Edu.z + Income.z + Female + (1|SubjectID) + (1|Issue),
                 data = merged_m, method="PB")
conf_mod <- lmer(Conformity ~  (MC.z + MajoritySupport.f + meta_d)^3 +
                     Polarized.z * MajoritySupport.f +
                   Age.z + Edu.z + Income.z + Female + (1|SubjectID) + (1|Issue),
                 data = merged_m)
conf_moral_sig <- mixed(Conformity ~  (Moral.f + MajoritySupport.f + meta_d)^3 +
                     Polarized.z * MajoritySupport.f +
                   Age.z + Edu.z + Income.z + Female + (1|SubjectID) + (1|Issue),
                 data = merged_m, method="PB")
conf_moral <- lmer(Conformity ~  (Moral.f + MajoritySupport.f + meta_d)^3 +
                     Polarized.z * MajoritySupport.f +
                   Age.z + Edu.z + Income.z + Female + (1|SubjectID) + (1|Issue),
                 data = merged_m)

mixed_summary(conf_mod_sig) %>% write_csv("Table_beh3_conf.csv")
#model_summary(conf_mod_sig)
```

Polarization and social support
```{r fig2c}
p1 <- plot_model(conf_mod, type="eff", terms=c("Polarized.z", "MajoritySupport.f"), title="Polarization") +
  geom_hline(yintercept=0, alpha=.3) 

p1$data$group <- factor(p1$data$group, levels=c("Minority","Neutral","Majority"))
p1 +
  labs(x = "Standardized Polarization", color="Social Support")
```

```{r conf_posthoc}
trend.mod <- emtrends(conf_mod, ~ MajoritySupport.f, "Polarized.z",
                      at = c(list(Polarized.z = seq(-1, 1))),
                      options = list(), lmer.df = 'satterthwaite')
summary(trend.mod, infer=c(TRUE, TRUE), null = 0)
```

Meta-d' and social support
```{r fig2d}
p1 <- plot_model(conf_mod, type="eff", terms=c("meta_d", "MajoritySupport.f"), title="Meta-d'") +
  geom_hline(yintercept=0, alpha=.3) 

p1$data$group <- factor(p1$data$group, levels=c("Minority","Neutral","Majority"))
p1 +
  labs(x = "Centered meta-d'", color="Social Support")
```

```{r maj_meta_posthoc}
trend.mod <- emtrends(conf_mod, ~ MajoritySupport.f, "meta_d",
                      at = c(list(Polarized.z = seq(-1, 1))),
                      options = list(), lmer.df = 'satterthwaite')
summary(trend.mod, infer=c(TRUE, TRUE), null = 0)
```

Moral conviciton and social support
```{r fig2e}
p1 <- plot_model(conf_mod, type="eff", terms=c("MC.z", "MajoritySupport.f"), title="Moral Conviction") +
  geom_hline(yintercept = 0, alpha=.3) + labs(x="Centered Moral Conviction")
p1 <- p1
p1$data$group <- factor(p1$data$group, levels=c("Minority","Neutral","Majority"))
p1 +
  labs(x = "Standardized Moral Conviction", y = "Conformity", color="Social Support")
```

```{r maj_mc_posthoc}
trend.mod <- emtrends(conf_mod, ~ MajoritySupport.f, "MC.z",
                      at = c(list(MC.z = seq(-1, 1))),
                      options = list(), lmer.df = 'satterthwaite')
summary(trend.mod, infer=c(TRUE, TRUE), null = 0)
```

Moral conviction, meta-d', and social support

```{r fig2f}
p1 <- plot_model(conf_mod, type="eff", terms = c("MC.z", "MajoritySupport.f", "meta_d[-.5, .5]"),
           title="Moral conviction * Meta-d'") +
  geom_hline(yintercept = 0, alpha=.3) + labs(x="Centered Moral Conviction")

p1$data$facet <- factor(p1$data$facet, levels=c(-0.5, 0.5),
                        labels=c("meta-d': -1 SD", "meta-d': +1 SD"))
p1$data$group <- factor(p1$data$group, levels=c("Minority","Neutral","Majority"))
p1 +
  labs(x = "Standardized Moral Conviction", color="Social Support")
```

```{r maj_mc_meta_posthoc}
trend.mod <- emtrends(conf_mod, ~ meta_d * MajoritySupport.f, "MC.z",
                      at = c(list(MC.z = seq(-1, 1)),
                             list(meta_d = c(-.5, .5))),
                      options = list(), lmer.df = 'satterthwaite')
summary(trend.mod, infer=c(TRUE, TRUE), null = 0)
```

Save fitted conformity values
```{r extract_conformity}
conf_intercepts <- ranef(conf_moral)$SubjectID
conf_intercepts$SubjectID <- rownames(conf_intercepts)
conf_intercepts <- conf_intercepts %>%
  select(SubjectID, everything()) %>%
  rename(Intercept = `(Intercept)`)

conf_predicts <- merged_m %>% select(SubjectID)
conf_predicts$fitted = fitted(conf_moral)
conf_predict_sum <- conf_predicts %>%
  group_by(SubjectID) %>%
  summarize(fitted = mean(fitted)) %>%
  ungroup()

conf_intercepts <- conf_intercepts %>%
  left_join(conf_predict_sum, by="SubjectID")
```

# ERP Analysis

## Import data
```{r import_erp_data}
m1 <- read_rds("data/eeg_issue_epn.RDS")
m2 <- read_rds("data/eeg_issue_mfn.RDS")
m3 <- read_rds("data/eeg_issue_lpp.RDS")
ms1 <- read_rds("data/eeg_social_epn.RDS")
ms2 <- read_rds("data/eeg_social_mfn.RDS")
ms3 <- read_rds("data/eeg_social_lpp.RDS")
ma1 <-  read_rds("data/eeg_photo_epn.RDS")
ma2 <- read_rds("data/eeg_photo_mfn.RDS")
ma3 <- read_rds("data/eeg_photo_lpp.RDS")
```

### Prep Difference waves
```{r diffs}
eeg_covars <- m1 %>%
  select(SubjectID:meta_d) %>%
  filter(!duplicated(select(., SubjectID)))
m1d <- m1 %>% 
  filter(Cluster2 != "Other") %>% 
  group_by(SubjectID, Subject, Moral, Cluster2) %>% 
  summarize(Amplitude = mean(Amplitude)) %>% 
  ungroup() %>% 
  pivot_wider(names_from=c(Moral), values_from="Amplitude") %>%
  mutate(MoralDif = (Moral - Nonmoral)) %>%
  dplyr::select(SubjectID, Cluster2, MoralDif) %>%
  pivot_wider(names_from = Cluster2, values_from = c(MoralDif) ) %>%
  left_join(eeg_covars, by=c("SubjectID"))
m2d <- m2 %>% 
  filter(Cluster2 != "Other") %>% 
  group_by(SubjectID, Subject, Moral, Cluster2) %>% 
  summarize(Amplitude = mean(Amplitude)) %>% 
  ungroup() %>% 
  pivot_wider(names_from=c(Moral), values_from="Amplitude") %>%
  mutate(MoralDif = (Moral - Nonmoral)) %>%
  dplyr::select(SubjectID, Cluster2, MoralDif) %>%
  pivot_wider(names_from = Cluster2, values_from = c(MoralDif) ) %>%
  left_join(eeg_covars, by=c("SubjectID"))
m3d <- m3 %>% 
  filter(Cluster2 != "Other") %>% 
  group_by(SubjectID, Subject, Moral, Cluster2) %>% 
  summarize(Amplitude = mean(Amplitude)) %>% 
  ungroup() %>% 
  pivot_wider(names_from=c(Moral), values_from="Amplitude") %>%
  mutate(MoralDif = (Moral - Nonmoral)) %>%
  dplyr::select(SubjectID, Cluster2, MoralDif) %>%
  pivot_wider(names_from = Cluster2, values_from = c(MoralDif) ) %>%
  left_join(eeg_covars, by=c("SubjectID"))
ms1d <- ms1 %>% 
  filter(Cluster2 != "Other") %>% 
  group_by(SubjectID, Subject, Moral.f, Congruent.f, Cluster2) %>% 
  summarize(Amplitude = mean(Amplitude)) %>% 
  ungroup() %>% 
  pivot_wider(names_from=c(Moral.f, Congruent.f), values_from="Amplitude") %>%
  mutate(Moral = (Moral_Congruent + Moral_Neutral + Moral_Incongruent -
                  Nonmoral_Congruent - Nonmoral_Neutral - Nonmoral_Incongruent)/3) %>%
  mutate(Congruent = (Moral_Congruent - Moral_Neutral +
                        Nonmoral_Congruent - Nonmoral_Neutral)/2) %>%
  mutate(Incongruent = (Moral_Incongruent - Moral_Neutral +
                        Nonmoral_Incongruent - Nonmoral_Neutral)/2) %>%
  mutate(MoralCongruent = (Moral_Congruent - Moral_Incongruent -
                             Nonmoral_Congruent + Nonmoral_Incongruent - 
                             Moral_Neutral + Nonmoral_Neutral)/3) %>%
  dplyr::select(SubjectID, Cluster2, Moral:MoralCongruent) %>%
  pivot_wider(names_from = Cluster2, values_from = c(Moral, Incongruent, Congruent, MoralCongruent) ) %>%
  left_join(eeg_covars, by=c("SubjectID"))
ms2d <- ms2 %>% 
  filter(Cluster2 != "Other") %>% 
  group_by(SubjectID, Subject, Moral.f, Congruent.f, Cluster2) %>% 
  summarize(Amplitude = mean(Amplitude)) %>% 
  ungroup() %>% 
  pivot_wider(names_from=c(Moral.f, Congruent.f), values_from="Amplitude") %>%
  mutate(Moral = (Moral_Congruent + Moral_Neutral + Moral_Incongruent -
                  Nonmoral_Congruent - Nonmoral_Neutral - Nonmoral_Incongruent)/3) %>%
  mutate(Congruent = (Moral_Congruent - Moral_Incongruent +
                        Nonmoral_Congruent - Nonmoral_Incongruent)/2) %>%
  mutate(Incongruent = (Moral_Incongruent - Moral_Neutral +
                        Nonmoral_Incongruent - Nonmoral_Neutral)/2) %>%
  mutate(MoralCongruent = (Moral_Congruent - Moral_Incongruent -
                             Nonmoral_Congruent + Nonmoral_Incongruent - 
                             Moral_Neutral + Nonmoral_Neutral)/3) %>%
  dplyr::select(SubjectID, Cluster2, Moral:MoralCongruent) %>%
  pivot_wider(names_from = Cluster2, values_from = c(Moral, Congruent, Incongruent, MoralCongruent) ) %>%
  left_join(eeg_covars, by=c("SubjectID"))
ms3d <- ms3 %>% 
  filter(Cluster2 != "Other") %>% 
  group_by(SubjectID, Subject, Moral.f, Congruent.f, Cluster2) %>% 
  summarize(Amplitude = mean(Amplitude)) %>% 
  ungroup() %>% 
  pivot_wider(names_from=c(Moral.f, Congruent.f), values_from="Amplitude") %>%
  mutate(Moral = (Moral_Congruent + Moral_Neutral + Moral_Incongruent -
                  Nonmoral_Congruent - Nonmoral_Neutral - Nonmoral_Incongruent)/3) %>%
  mutate(Congruent = (Moral_Congruent - Moral_Incongruent +
                        Nonmoral_Congruent - Nonmoral_Incongruent)/2) %>%
  mutate(Incongruent = (Moral_Incongruent - Moral_Neutral +
                        Nonmoral_Incongruent - Nonmoral_Neutral)/2) %>%
  mutate(MoralCongruent = (Moral_Congruent - Moral_Incongruent -
                             Nonmoral_Congruent + Nonmoral_Incongruent - 
                             Moral_Neutral + Nonmoral_Neutral)/3) %>%
  dplyr::select(SubjectID, Cluster2, Moral:MoralCongruent) %>%
  pivot_wider(names_from = Cluster2, values_from = c(Moral, Congruent, Incongruent, MoralCongruent) ) %>%
  left_join(eeg_covars, by=c("SubjectID"))

ma1d <- ma1 %>% 
  filter(Cluster2 != "Other") %>% 
  group_by(SubjectID, Subject, Moral.f, Agree.f, Cluster2) %>% 
  summarize(Amplitude = mean(Amplitude)) %>% 
  ungroup() %>% 
  pivot_wider(names_from=c(Moral.f, Agree.f), values_from="Amplitude") %>%
  mutate(Moral = (Moral_Agree + Moral_Disagree -
                  Nonmoral_Agree - Nonmoral_Disagree)/2) %>%
  mutate(Agree = (Moral_Agree - Moral_Disagree +
                        Nonmoral_Agree - Nonmoral_Disagree)/2) %>%
  mutate(MoralAgree = (Moral_Agree - Moral_Disagree -
                             Nonmoral_Agree + Nonmoral_Disagree)/2) %>%
  dplyr::select(SubjectID, Cluster2, Moral:MoralAgree) %>%
  pivot_wider(names_from = Cluster2, values_from = c(Moral, Agree, MoralAgree) ) %>%
  left_join(eeg_covars, by=c("SubjectID"))

ma2d <- ma2 %>% 
  filter(Cluster2 != "Other") %>% 
  group_by(SubjectID, Subject, Moral.f, Agree.f, Cluster2) %>% 
  summarize(Amplitude = mean(Amplitude)) %>% 
  ungroup() %>% 
  pivot_wider(names_from=c(Moral.f, Agree.f), values_from="Amplitude") %>%
  mutate(Moral = (Moral_Agree + Moral_Disagree -
                  Nonmoral_Agree - Nonmoral_Disagree)/2) %>%
  mutate(Agree = (Moral_Agree - Moral_Disagree +
                        Nonmoral_Agree - Nonmoral_Disagree)/2) %>%
  mutate(MoralAgree = (Moral_Agree - Moral_Disagree -
                             Nonmoral_Agree + Nonmoral_Disagree)/2) %>%
  dplyr::select(SubjectID, Cluster2, Moral:MoralAgree) %>%
  pivot_wider(names_from = Cluster2, values_from = c(Moral, Agree, MoralAgree) ) %>%
  left_join(eeg_covars, by=c("SubjectID"))

ma3d <- ma3 %>% 
  filter(Cluster2 != "Other") %>% 
  group_by(SubjectID, Subject, Moral.f, Agree.f, Cluster2) %>% 
  summarize(Amplitude = mean(Amplitude)) %>% 
  ungroup() %>% 
  pivot_wider(names_from=c(Moral.f, Agree.f), values_from="Amplitude") %>%
  mutate(Moral = (Moral_Agree + Moral_Disagree -
                  Nonmoral_Agree - Nonmoral_Disagree)/2) %>%
  mutate(Agree = (Moral_Agree - Moral_Disagree +
                        Nonmoral_Agree - Nonmoral_Disagree)/2) %>%
  mutate(MoralAgree = (Moral_Agree - Moral_Disagree -
                             Nonmoral_Agree + Nonmoral_Disagree)/2) %>%
  dplyr::select(SubjectID, Cluster2, Moral:MoralAgree) %>%
  pivot_wider(names_from = Cluster2, values_from = c(Moral, Agree, MoralAgree) ) %>%
  left_join(eeg_covars, by=c("SubjectID"))
```

## Issue

### EPN: 100-200
```{r iss_epn_mods}
m1.mlm.post.e <- mixed(Amplitude ~ Moral + Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = m1 %>% filter(Cluster2 == "Posterior"), method="PB")
m1.mlm.post.e2 <- mixed(Amplitude ~ (Moral + meta_d)^2 +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = m1 %>% filter(Cluster2 == "Posterior"), method="PB")

m1.mlm.fc.e <- mixed(Amplitude ~ Moral + Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = m1 %>% filter(Cluster2 == "Frontal"), method="PB")
m1.mlm.fc.e2 <- mixed(Amplitude ~ (Moral + meta_d)^2 + Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = m1 %>% filter(Cluster2 == "Frontal"), method="PB")

anova(m1.mlm.post.e, m1.mlm.post.e2)
```

```{r}
eeg_summary(m1.mlm.post.e) 
mixed_summary(m1.mlm.post.e) %>% write_csv("Table_erp_iss_epn.csv")
```

```{r}
eeg_summary(m1.mlm.fc.e2) 
mixed_summary(m1.mlm.fc.e2) %>% write_csv("Table_erp_iss_fn1.csv")
```

```{r}
trend.mod <- emtrends(m1.mlm.fc.e2, ~Moral, "meta_d",
                       at = c(list(meta_d = seq(-.5, 2))),
                      options = list(), lmer.df = "satterthwaite")
 summary(trend.mod, infer = c(TRUE, TRUE), null=0)
```


### MFN/N2: 300-500
```{r iss_mfn_mods}
m2.mlm.fc.e <- mixed(Amplitude ~ Moral + Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = m2 %>% filter(Cluster2 == "Frontal"), method="PB")
m2.mlm.fc.e2 <- mixed(Amplitude ~ (Moral + meta_d)^2 + Female + Age.z +
                         (1|Subject) + (1|Channel),
                       data = m2 %>% filter(Cluster2 == "Frontal"),
                     control = lmerControl(optimizer = "bobyqa"), method="PB")
```

```{r}
eeg_summary(m2.mlm.fc.e2) 
mixed_summary(m2.mlm.fc.e2) %>% write_csv("Table_erp_iss_mfn.csv")
```

```{r}
trend.mod <- emtrends(m2.mlm.fc.e2, ~Moral, "meta_d",
                       at = c(list(meta_d = seq(-.5, 2))),
                      options = list(), lmer.df = "satterthwaite")
 summary(trend.mod, infer = c(TRUE, TRUE), null=0)
```


### LPP: 600-800
```{r iss_lpp_mods}
m3.mlm.post.e <- mixed(Amplitude ~ Moral + Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = m3 %>% filter(Cluster2 == "Posterior"), method="PB")
m3.mlm.post.e2 <- mixed(Amplitude ~ (Moral + meta_d)^2 +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = m3 %>% filter(Cluster2 == "Posterior"), method="PB")

m3.mlm.fc.e <- mixed(Amplitude ~ Moral + Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = m3 %>% filter(Cluster2 == "Frontal"), method="PB")
m3.mlm.fc.e2 <- mixed(Amplitude ~ (Moral + meta_d)^2 + Female + Age.z +
                         (1|Subject) + (1|Channel),
                       data = m3 %>% filter(Cluster2 == "Frontal"),
                     control = lmerControl(optimizer = "bobyqa"), method="PB")
```

```{r}
anova(m3.mlm.post.e, m3.mlm.post.e2)
```

```{r}
eeg_summary(m3.mlm.post.e)
```

```{r}
anova(m3.mlm.fc.e, m3.mlm.fc.e2)
```

```{r}
eeg_summary(m3.mlm.fc.e2) 
mixed_summary(m3.mlm.fc.e2) %>% write_csv("Table_erp_iss_lpp.csv")
```

```{r}
trend.mod <- emtrends(m3.mlm.fc.e2, ~Moral, "meta_d",
                       at = c(list(meta_d = seq(-.5, 2))),
                      options = list(), lmer.df = "satterthwaite")
 summary(trend.mod, infer = c(TRUE, TRUE), null=0)
```


#### Conformity
```{r}
m1d_m_fc <- summary(lm(Frontal ~ Conformity + Age.z + Female, data = m1d))$coefficients[2,]
m1d_m_post <- summary(lm(Posterior ~ Conformity + Age.z + Female, data = m1d))$coefficients[2,]

m2d_m_fc <- summary(lm(Frontal ~ Conformity + Age.z + Female, data = m2d))$coefficients[2,]
m2d_m_post <- summary(lm(Posterior ~ Conformity + Age.z + Female, data = m2d))$coefficients[2,]

m3d_m_fc <- summary(lm(Frontal ~ Conformity + Age.z + Female, data = m3d))$coefficients[2,]
m3d_m_post <- summary(lm(Posterior ~ Conformity + Age.z + Female, data = m3d))$coefficients[2,]


md1_lm <- rbind(m1d_m_fc, m1d_m_post)
md1_lm
md2_lm <- rbind(m2d_m_fc, m2d_m_post)
md2_lm
md3_lm <- rbind(m3d_m_fc, m3d_m_post)
md3_lm
```

## Social Information
```{r}
ms1m <- ms1 %>% 
  group_by(Subject, Moral, Congruent.f, Cluster2, 
           meta_d, Age.z, Income.z, Edu.z, Female) %>%
  summarize(Amplitude = mean(Amplitude)) %>%
  ungroup()
ms2m <- ms2 %>% 
  group_by(Subject, Moral, Congruent.f, Cluster2, 
           meta_d, Age.z, Income.z, Edu.z, Female) %>%
  summarize(Amplitude = mean(Amplitude)) %>%
  ungroup()
ms3m <- ms3 %>% 
  group_by(Subject, Moral, Congruent.f, Cluster2, 
           meta_d, Age.z, Income.z, Edu.z, Female) %>%
  summarize(Amplitude = mean(Amplitude)) %>%
  ungroup()
```

### EPN: 125-175
```{r soc_epn_mods}
epn <- ms1 %>% filter(Cluster2 %in% c("Posterior", "Frontal")) %>%
  select(Subject, Channel, Cluster2, Amplitude, Moral.f, Congruent.f, Female, Age.z, meta_d) %>%
  drop_na()
ms1.mlm.post.e <- mixed(Amplitude ~ Moral.f * Congruent.f  +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = epn %>% filter(Cluster2 == "Posterior"), method="PB")
ms1.mlm.post.e2 <- mixed(Amplitude ~ (Moral.f + Congruent.f + meta_d)^2 +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = epn %>% filter(Cluster2 == "Posterior"), method="PB")

ms1.mlm.fc.e <- mixed(Amplitude ~ Moral.f * Congruent.f  +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = epn %>% filter(Cluster2 == "Frontal"), method="PB")
ms1.mlm.fc.e2 <- mixed(Amplitude ~ (Moral.f + Congruent.f + meta_d)^2 +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = epn %>% filter(Cluster2 == "Frontal"), method="PB")
```

```{r}
eeg_summary(ms1.mlm.post.e)
mixed_summary(ms1.mlm.fc.e2) %>% write_csv("Table_erp_soc_epn.csv")
```

```{r}
emmeans(ms1.mlm.post.e2, pairwise ~ Moral.f | Congruent.f)
```

```{r}
anova(ms1.mlm.fc.e, ms1.mlm.fc.e2)
```

```{r}
eeg_summary(ms1.mlm.fc.e2)
```

### MFN/N2: 200-300
```{r, soc_mfn_mods, results="hide"}
mfn <- ms2 %>% filter(Cluster2 %in% c("Posterior", "Frontal")) %>%
  select(Subject, Channel, Cluster2, Amplitude, Moral.f, Congruent.f, Female, Age.z, meta_d) %>%
  drop_na()

ms2.mlm.post.e <- mixed(Amplitude ~ Moral.f * Congruent.f  +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = mfn %>% filter(Cluster2=="Posterior"), method="PB")
ms2.mlm.post.e2 <- mixed(Amplitude ~ (Moral.f + Congruent.f + meta_d)^2 +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = mfn %>% filter(Cluster2=="Posterior"), method="PB")

ms2.mlm.fc.e <- mixed(Amplitude ~ Moral.f * Congruent.f  +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = mfn %>% filter(Cluster2=="Frontal"), method="PB")
ms2.mlm.fc.e2 <- mixed(Amplitude ~ (Moral.f + Congruent.f + meta_d)^2 +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = mfn %>% filter(Cluster2=="Frontal"), method="PB")
```

```{r}
anova(ms2.mlm.fc.e, ms2.mlm.fc.e2)
```

```{r}
ms2.mlm.fc.e2
```

```{r}
eeg_summary(ms2.mlm.fc.e2)
mixed_summary(ms2.mlm.fc.e2) %>% write_csv("Table_erp_soc_mfn.csv")
```

```{r}
emmeans(ms2.mlm.fc.e2, pairwise ~ Congruent.f )
```

```{r}
emmeans(ms2.mlm.fc.e2, pairwise ~ Moral.f | Congruent.f)
```

```{r}
trend.mod <- emtrends(ms2.mlm.fc.e2, ~Moral.f, "meta_d",
                       at = c(list(meta_d = seq(-.5, 2))),
                      options = list(), lmer.df = "satterthwaite")
 summary(trend.mod, infer = c(TRUE, TRUE), null=0)
```

```{r}
trend.mod <- emtrends(ms2.mlm.fc.e2, ~Congruent.f, "meta_d",
                       at = c(list(meta_d = seq(-.5, 2))),
                      options = list(), lmer.df = "satterthwaite")
 summary(trend.mod, infer = c(TRUE, TRUE), null=0)
```


### LPP: 300-500
```{r, soc_lpp_mods}

lpp <- ms3 %>% filter(Cluster2 %in% c("Posterior", "Frontal")) %>%
  select(Subject, Channel, Cluster2, Amplitude, Moral.f, Congruent.f, Female, Age.z, meta_d) %>%
  drop_na()

ms3.mlm.post.e <- mixed(Amplitude ~ Moral.f * Congruent.f  +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = lpp %>% filter(Cluster2 == "Posterior"), method="PB")
ms3.mlm.post.e2 <- mixed(Amplitude ~ (Moral.f + Congruent.f + meta_d)^2 +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = lpp %>% filter(Cluster2 == "Posterior"), method="PB")

ms3.mlm.fc.e <- mixed(Amplitude ~ Moral.f * Congruent.f  +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = lpp %>% filter(Cluster2 == "Frontal"), method="PB")
ms3.mlm.fc.e2 <- mixed(Amplitude ~ (Moral.f + Congruent.f + meta_d)^2 +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = lpp %>% filter(Cluster2 == "Frontal"), method="PB")
```

```{r}
anova(ms3.mlm.post.e, ms3.mlm.post.e2)
```

```{r}
emmeans(ms3.mlm.post.e2, pairwise ~ Congruent.f | Moral.f)
```

```{r}
emmeans(ms3.mlm.post.e2, pairwise ~ Moral.f | Congruent.f)
```


```{r}
eeg_summary(ms3.mlm.post.e2)
```

```{r}
trend.mod <- emtrends(ms3.mlm.post.e2, ~Moral.f, "meta_d",
                       at = c(list(meta_d = seq(-.5, 2))),
                      options = list(), lmer.df = "satterthwaite")
 summary(trend.mod, infer = c(TRUE, TRUE), null=0)
```

```{r}
anova(ms3.mlm.fc.e, ms3.mlm.fc.e2)
```

```{r}
eeg_summary(ms3.mlm.fc.e2)
mixed_summary(ms3.mlm.fc.e2) %>% write_csv("Table_erp_soc_lpp.csv")
```

```{r}
emmeans(ms3.mlm.fc.e2, pairwise ~ Congruent.f | Moral.f)
```

```{r}
emmeans(ms3.mlm.fc.e2, pairwise ~ Moral.f | Congruent.f)
```


#### Conformity
```{r}
ms1d_m_fc <- summary(lm(Moral_Frontal ~ Conformity + Age.z + Female, data = ms1d))$coefficients[2,]
ms1d_m_post <- summary(lm(Moral_Posterior ~ Conformity + Age.z + Female, data = ms1d))$coefficients[2,]
ms1d_c_fc <- summary(lm(Congruent_Frontal ~ Conformity + Age.z + Female, data = ms1d))$coefficients[2,]
ms1d_c_post <- summary(lm(Congruent_Posterior ~ Conformity + Age.z + Female, data = ms1d))$coefficients[2,]
ms1d_i_fc <- summary(lm(Incongruent_Frontal ~ Conformity + Age.z + Female, data = ms1d))$coefficients[2,]
ms1d_i_post <- summary(lm(Incongruent_Posterior ~ Conformity + Age.z + Female, data = ms1d))$coefficients[2,]
ms1d_mc_fc <- summary(lm(MoralCongruent_Frontal ~ Conformity + Age.z + Female, data = ms1d))$coefficients[2,]
ms1d_mc_post <- summary(lm(MoralCongruent_Posterior ~ Conformity + Age.z + Female, data = ms1d))$coefficients[2,]

ms2d_m_fc <- summary(lm(Moral_Frontal ~ Conformity + Age.z + Female, data = ms2d))$coefficients[2,]
ms2d_m_post <- summary(lm(Moral_Posterior ~ Conformity + Age.z + Female, data = ms2d))$coefficients[2,]
ms2d_c_fc <- summary(lm(Congruent_Frontal ~ Conformity + Age.z + Female, data = ms2d))$coefficients[2,]
ms2d_c_post <- summary(lm(Congruent_Posterior ~ Conformity + Age.z + Female, data = ms2d))$coefficients[2,]
ms2d_i_fc <- summary(lm(Incongruent_Frontal ~ Conformity + Age.z + Female, data = ms2d))$coefficients[2,]
ms2d_i_post <- summary(lm(Incongruent_Posterior ~ Conformity + Age.z + Female, data = ms2d))$coefficients[2,]
ms2d_mc_fc <- summary(lm(MoralCongruent_Frontal ~ Conformity + Age.z + Female, data = ms2d))$coefficients[2,]
ms2d_mc_post <- summary(lm(MoralCongruent_Posterior ~ Conformity + Age.z + Female, data = ms2d))$coefficients[2,]

ms3d_m_fc <- summary(lm(Moral_Frontal ~ Conformity + Age.z + Female, data = ms3d))$coefficients[2,]
ms3d_m_post <- summary(lm(Moral_Posterior ~ Conformity + Age.z + Female, data = ms3d))$coefficients[2,]
ms3d_c_fc <- summary(lm(Congruent_Frontal ~ Conformity + Age.z + Female, data = ms3d))$coefficients[2,]
ms3d_c_post <- summary(lm(Congruent_Posterior ~ Conformity + Age.z + Female, data = ms3d))$coefficients[2,]
ms3d_i_fc <- summary(lm(Incongruent_Frontal ~ Conformity + Age.z + Female, data = ms3d))$coefficients[2,]
ms3d_i_post <- summary(lm(Incongruent_Posterior ~ Conformity + Age.z + Female, data = ms3d))$coefficients[2,]
ms3d_mc_fc <- summary(lm(MoralCongruent_Frontal ~ Conformity + Age.z + Female, data = ms3d))$coefficients[2,]
ms3d_mc_post <- summary(lm(MoralCongruent_Posterior ~ Conformity + Age.z + Female, data = ms3d))$coefficients[2,]

msd1_lm <- rbind(ms1d_m_fc, ms1d_m_post,
                 ms1d_c_fc, ms1d_c_post,
                 ms1d_i_fc, ms1d_i_post,
                 ms1d_mc_fc, ms1d_mc_post)

msd2_lm <- rbind(ms2d_m_fc, ms2d_m_post,
                 ms2d_c_fc, ms2d_c_post,
                 ms2d_i_fc, ms2d_i_post,
                 ms2d_mc_fc, ms2d_mc_post)

msd3_lm <- rbind(ms3d_m_fc, ms3d_m_post,
                 ms3d_c_fc, ms3d_c_post,
                 ms3d_i_fc, ms3d_i_post,
                 ms3d_mc_fc, ms3d_mc_post)
```

```{r}
msd1_lm

msd2_lm

msd3_lm
```

```{r}
soc_mfn <- ms2d %>% select(Moral_Frontal, Conformity, Age.z, Female) %>% drop_na()
mfn_mor_conf = lm(Moral_Frontal ~ Conformity + Age.z + Female, data = soc_mfn)
#model_summary(mfn_mor_conf)
mfn_mor = lm(Moral_Frontal ~ Age.z + Female, data=soc_mfn)
mfn_conf = lm(Conformity ~ Age.z + Female, data=soc_mfn)
mfn_mc <- tibble(Amplitude = resid(mfn_mor),
                 Conformity = resid(mfn_conf))
ggplot(mfn_mc, aes(Conformity, Amplitude)) + geom_point() +
  geom_smooth(method="lm") + ggtitle("MFN (Moral-Nonmoral)")
```


## Photo

### EPN: 100-200

```{r pic_epn_mods}
epn <- ma1 %>% filter(Cluster2 %in% c("Posterior", "Frontal")) %>%
  select(Subject, Channel, Cluster2, Amplitude, Moral.f, Agree.f, Female, Age.z, meta_d) %>%
  drop_na()
ma1.mlm.post.e <- mixed(Amplitude ~ Moral.f * Agree.f +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = epn %>% filter(Cluster2 == "Posterior"), method="PB")

ma1.mlm.post.e2 <- mixed(Amplitude ~ (Moral.f + Agree.f + meta_d)^2 +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = epn %>% filter(Cluster2 == "Posterior"), method="PB")

ma1.mlm.fc.e <- mixed(Amplitude ~ Moral.f * Agree.f +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = epn %>% filter(Cluster2 == "Frontal"),
                     control = lmerControl(optimizer = "bobyqa"), method="PB")
ma1.mlm.fc.e2 <- mixed(Amplitude ~ (Moral.f + Agree.f + meta_d)^2 +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = epn %>% filter(Cluster2 == "Frontal"), method="PB")
```

```{r}
anova(ma1.mlm.post.e, ma1.mlm.post.e2)
```

```{r}
eeg_summary(ma1.mlm.post.e) 
mixed_summary(ma1.mlm.post.e) %>% write_csv("Table_erp_pic_epn.csv")
```

```{r}
emmeans(ma1.mlm.post.e, pairwise ~  Agree.f | Moral.f)
```

```{r}
anova(ma1.mlm.fc.e, ma1.mlm.fc.e2)
```

```{r}
eeg_summary(ma1.mlm.fc.e)
```


```{r}
emmeans(ma1.mlm.fc.e, pairwise ~ Agree.f | Moral.f, data = ma1 %>% filter(Cluster2 == "Frontal"))
```

### MFN/N2: 200-400
```{r pic_mfn_mods}
mfn <- ma2 %>% filter(Cluster2 %in% c("Posterior", "Frontal")) %>%
  select(Subject, Channel, Cluster2, Amplitude, Moral.f, Agree.f, Female, Age.z, meta_d) %>%
  drop_na()

ma2.mlm.post.e <- mixed(Amplitude ~ Moral.f * Agree.f +
                          Female + Age.z + 
                          (1|Subject) + (1|Channel),
                        data = mfn %>% filter(Cluster2 == "Posterior"))
ma2.mlm.post.e2 <- mixed(Amplitude ~ (Moral.f + Agree.f + meta_d)^2 +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = mfn %>% filter(Cluster2 == "Posterior"))

ma2.mlm.fc.e <- mixed(Amplitude ~ Moral.f * Agree.f +
                          Female + Age.z + 
                          (1|Subject) + (1|Channel),
                        data = mfn %>% filter(Cluster2 == "Frontal"))
ma2.mlm.fc.e2 <- mixed(Amplitude ~ (Moral.f + Agree.f + meta_d)^2 +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = mfn %>% filter(Cluster2 == "Frontal"))
```

```{r}
anova(ma2.mlm.post.e, ma2.mlm.post.e2)
```

```{r}
anova(ma2.mlm.fc.e, ma2.mlm.fc.e2)
```

```{r}
eeg_summary(ma2.mlm.fc.e2) 
mixed_summary(ma2.mlm.fc.e2) %>% write_csv("Table_erp_pic_mfn.csv")
```

```{r}
trend.mod <- emtrends(ma2.mlm.fc.e2, ~Moral.f, "meta_d", 
                      at = c(list(meta_d = seq(-.5, 2))),
                      options = list(), lmer.df = "satterthwaite")
summary(trend.mod, infer = c(TRUE, TRUE), null=0)
```

### LPP: 400-600 
```{r pic_lpp_mods}
lpp <- ma2 %>% filter(Cluster2 %in% c("Posterior", "Frontal")) %>%
  select(Subject, Channel, Cluster2, Amplitude, Moral.f, Agree.f, Female, Age.z, meta_d) %>%
  drop_na()

ma3.mlm.post.e <- mixed(Amplitude ~ Moral.f * Agree.f +
                          Female + Age.z + 
                          (1|Subject) + (1|Channel),
                        data = lpp %>% filter(Cluster2 == "Posterior"))
ma3.mlm.post.e2 <- mixed(Amplitude ~ (Moral.f + Agree.f + meta_d)^2 +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = lpp %>% filter(Cluster2 == "Posterior"))


ma3.mlm.fc.e <- mixed(Amplitude ~ Moral.f * Agree.f +
                          Female + Age.z + 
                          (1|Subject) + (1|Channel),
                        data = lpp %>% filter(Cluster2 == "Frontal"))
ma3.mlm.fc.e2 <- mixed(Amplitude ~ (Moral.f + Agree.f + meta_d)^2 +
                          Female + Age.z +
                          (1|Subject) + (1|Channel),
                        data = lpp %>% filter(Cluster2 == "Frontal"))
```

```{r}
anova(ma3.mlm.post.e, ma3.mlm.post.e2)
```

```{r}
eeg_summary(ma3.mlm.post.e)
```


```{r}
anova(ma3.mlm.fc.e, ma3.mlm.fc.e2)
```

```{r}
eeg_summary(ma3.mlm.fc.e) 
mixed_summary(ma3.mlm.fc.e) %>% write_csv("Table_erp_pic_lpp.csv")
```


#### Conformity
```{r}
ma1d_m_fc <- summary(lm(Moral_Frontal ~ Conformity + Age.z + Female, data = ma1d))$coefficients[2,]
ma1d_m_post <- summary(lm(Moral_Posterior ~ Conformity + Age.z + Female, data = ma1d))$coefficients[2,]
ma1d_a_fc <- summary(lm(Agree_Frontal ~ Conformity + Age.z + Female, data = ma1d))$coefficients[2,]
ma1d_a_post <- summary(lm(Agree_Posterior ~ Conformity + Age.z + Female, data = ma1d))$coefficients[2,]
ma1d_ma_fc <- summary(lm(MoralAgree_Frontal ~ Conformity + Age.z + Female, data = ma1d))$coefficients[2,]
ma1d_ma_post <- summary(lm(MoralAgree_Posterior ~ Conformity + Age.z + Female, data = ma1d))$coefficients[2,]

ma2d_m_fc <- summary(lm(Moral_Frontal ~ Conformity + Age.z + Female, data = ma2d))$coefficients[2,]
ma2d_m_post <- summary(lm(Moral_Posterior ~ Conformity + Age.z + Female, data = ma2d))$coefficients[2,]
ma2d_a_fc <- summary(lm(Agree_Frontal ~ Conformity + Age.z + Female, data = ma2d))$coefficients[2,]
ma2d_a_post <- summary(lm(Agree_Posterior ~ Conformity + Age.z + Female, data = ma2d))$coefficients[2,]
ma2d_ma_fc <- summary(lm(MoralAgree_Frontal ~ Conformity + Age.z + Female, data = ma2d))$coefficients[2,]
ma2d_ma_post <- summary(lm(MoralAgree_Posterior ~ Conformity + Age.z + Female, data = ma2d))$coefficients[2,]

ma3d_m_fc <- summary(lm(Moral_Frontal ~ Conformity + Age.z + Female, data = ma3d))$coefficients[2,]
ma3d_m_post <- summary(lm(Moral_Posterior ~ Conformity + Age.z + Female, data = ma3d))$coefficients[2,]
ma3d_a_fc <- summary(lm(Agree_Frontal ~ Conformity + Age.z + Female, data = ma3d))$coefficients[2,]
ma3d_a_post <- summary(lm(Agree_Posterior ~ Conformity + Age.z + Female, data = ma3d))$coefficients[2,]
ma3d_ma_fc <- summary(lm(MoralAgree_Frontal ~ Conformity + Age.z + Female, data = ma3d))$coefficients[2,]
ma3d_ma_post <- summary(lm(MoralAgree_Posterior ~ Conformity + Age.z + Female, data = ma3d))$coefficients[2,]

mad1_lm <- rbind(ma1d_m_fc, ma1d_m_post,
                 ma1d_a_fc, ma1d_a_post,
                 ma1d_ma_fc, ma1d_ma_post)

mad2_lm <- rbind(ma2d_m_fc, ma2d_m_post,
                 ma2d_a_fc, ma2d_a_post,
                 ma2d_ma_fc, ma2d_ma_post)

mad3_lm <- rbind(ma3d_m_fc, ma3d_m_post,
                 ma3d_a_fc, ma3d_a_post,
                 ma3d_ma_fc, ma3d_ma_post)
```

```{r}
mad1_lm
mad2_lm
mad3_lm
```


```{r}
pic_epn <- ma1d %>% select(Moral_Posterior, Conformity, Age.z, Female) %>% drop_na()
epn_mor_conf = lm(Moral_Posterior ~ Conformity + Age.z + Female, data = pic_epn)
#model_summary(epn_mor_conf)
epn_mor = lm(Moral_Posterior ~ Age.z + Female, data=pic_epn)
epn_conf = lm(Conformity ~ Age.z + Female, data=pic_epn)
epn_mc <- tibble(Amplitude = resid(epn_mor),
                 Conformity = resid(epn_conf))
ggplot(epn_mc, aes(Conformity, Amplitude)) + geom_point() +
  geom_smooth(method="lm")+ ggtitle("EPN (Moral-Nonmoral)")
```


